Calculating impedances for CMA and CA areas from the GSS surveys

### 2024-11-29 data-raw/02-calculating-impedances.Rmd
Adding the weight variable to the impedance data set.

```{r}
gss_impedances <- gss_episodes[,c("PUMFID","DURATION",
                                  "origin","destination","Province","Pop_centre","orig_label",
                                  "dest_label","YEAR","MODE","f_name",
                                  "f","est_1","est_2","loglik","aic","bic","count")]
```

>>>>

```{r}
gss_impedances <- gss_episodes[,c("PUMFID","WGHT_EPI","DURATION",
                                  "origin","destination","Province","Pop_centre","orig_label",
                                  "dest_label","YEAR","MODE","f_name",
                                  "f","est_1","est_2","loglik","aic","bic","count")]
```
